Report

### 2021-05-31 Rmd/report.Rmd
Add sample sizes to plots

# vocabulary
participants %>% 
	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot(aes(lp, vocab_size, colour = lp, fill = lp)) +
	facet_wrap(location~age_group) +
	geom_violin(position = position_dodge(width = 0.75)) + 
	# geom_point(shape = 1, colour = "black", alpha = 0.5, size = 3, stroke = 1,
	# 		   position = position_jitter(width = 0.1, seed = 888)) +
	geom_boxplot(width = 0.1, colour = "black", fill = "white", outlier.colour = NA,
				 position = position_dodge(width = 0.75)) +
		geom_text(data = sample_size,
			  aes(x = 1.5, y = 0.95, label = paste0("n = ", n),
			  	colour = "black", fill = "black"), show.legend = FALSE) +
	labs(y = "Receptive vocabulary size (L1)", colour = "Group", fill = "Group") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	theme(legend.title = element_blank(),
		  legend.position = "none",
		  axis.title.x = element_blank(),
		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "vocabulary.png"))

@@

gaze %>% 
	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
	left_join(select(participants, participant, age_group, location)) %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(participant, lp, trial_type, age_group, location) %>% 
	summarise(
		prop = mean(prop, na.rm = TRUE),
		.groups = "drop"
	) %>% 
	drop_na() %>% 
	ggplot(aes(trial_type, prop, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_violin(position = position_dodge(width = 0.75)) +
	#stat_slab(position = position_nudge(x = 0.25)) +
	#geom_point(size = 2, shape = 1, stroke = 1, position = position_jitter(width = 0.1)) +
	geom_boxplot(aes(group = interaction(age_group, trial_type)), width = 0.1, outlier.colour = NA,
				 position = position_dodge(width = 0.75), colour = "black", fill = "white") +
	geom_text(data = sample_size,
			  aes(x = 1, y = 0.95, label = paste0("n = ", n),
			  	colour = "black", fill = "black"), show.legend = FALSE) +
	labs(x = "Trial type", y = "Target looking / Total looking", colour = "Condition", fill = "Condition") + 
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	theme(legend.position = "none",
		  axis.title.x = element_blank(),
		  axis.text.x = element_text(angle = 30, vjust = 1, hjust = 1),
		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "gaze_trial_age.png"))

@@

```{r fixed_effects_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
confint.merMod(fit, method = "Wald") %>% 
	as.data.frame() %>% 
	clean_names() %>% 
	drop_na(x2_5_percent) %>%
	rownames_to_column("term") %>% 
	right_join(clean_names(tidy(fit, effects = "fixed"))) %>% 
	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
		   statistic, df, p_value) %>% 
	gt() %>% 
	fmt_number(2:7) %>% 
	fmt_number(8, decimals = 3) %>% 
	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
	cols_label(
		term = md("**Predictor**"),
		estimate = md("**Estimate**"),
		std_error = md("**SE**"),
		conf_lower = md("**CI<sub>95%</sub>**"),
		statistic = md("***t***"),
		df = md("**df**"),
		p_value = md("***p***")
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#F9E3D6")
		),
		locations = cells_body(
			columns = everything(),
			rows = p_value < 0.05
		)
	)
```

@@

augment(fit) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	ggplot(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(fun = mean, geom = "line", size = 1) +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n),
			  	colour = "black", fill = "black"), show.legend = FALSE) +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) + 
	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
	theme_custom() +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7)
	)
```

>>>>

# vocabulary
participants %>% 
	left_join(distinct(attrition, participant, age_group, valid_participant)) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot() +
	facet_wrap(location~age_group) +
	geom_violin(position = position_dodge(width = 0.75),
				aes(lp, vocab_size, colour = lp, fill = lp)) + 
	# geom_point(shape = 1, colour = "black", alpha = 0.5, size = 3, stroke = 1,
	# 		   position = position_jitter(width = 0.1, seed = 888)) +
	geom_boxplot(aes(lp, vocab_size, colour = lp, fill = lp),
				 width = 0.1, colour = "black", fill = "white", outlier.colour = NA,
				 position = position_dodge(width = 0.75)) +
	geom_text(data = sample_size,
			  aes(x = 1, y = 0.95, label = paste0("n = ", n)),
			  colour = "black", fill = "black", show.legend = FALSE) +
	labs(y = "Receptive vocabulary size (L1)", colour = "Group", fill = "Group") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	theme(legend.title = element_blank(),
		  legend.position = "none",
		  axis.title.x = element_blank(),
		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "vocabulary.png"))

@@

gaze %>% 
	left_join(select(attrition, participant, age_group, valid_trial, valid_participant)) %>% 
	left_join(select(participants, participant, age_group, location)) %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(participant, lp, trial_type, age_group, location) %>% 
	summarise(
		prop = mean(prop, na.rm = TRUE),
		.groups = "drop"
	) %>% 
	drop_na() %>% 
	ggplot() +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_violin(aes(trial_type, prop, colour = trial_type, fill = trial_type),
				position = position_dodge(width = 0.75)) +
	#stat_slab(position = position_nudge(x = 0.25)) +
	#geom_point(size = 2, shape = 1, stroke = 1, position = position_jitter(width = 0.1)) +
	geom_boxplot(aes(trial_type, prop, colour = trial_type, fill = trial_type,
					 group = interaction(age_group, trial_type)),
				 width = 0.1, outlier.colour = NA,
				 position = position_dodge(width = 0.75),
				 colour = "black", fill = "white") +
	geom_text(data = sample_size,
			  aes(x = 1, y = 0.95, label = paste0("n = ", n)),
			  colour = "black", fill = "black", show.legend = FALSE) +
	labs(x = "Trial type", y = "Target looking / Total looking", colour = "Condition", fill = "Condition") + 
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	theme(legend.position = "none",
		  axis.title.x = element_blank(),
		  axis.text.x = element_text(angle = 30, vjust = 1, hjust = 1),
		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "gaze_trial_age.png"))

@@

```{r fixed_effects_table, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
main_effects <- confint.merMod(fit, method = "Wald") %>% 
	as.data.frame() %>% 
	clean_names() %>% 
	drop_na(x2_5_percent) %>%
	rownames_to_column("term") %>% 
	right_join(clean_names(tidy(fit, effects = "fixed"))) %>% 
	select(term, estimate, std_error, conf_lower = x2_5_percent, conf_upper = x97_5_percent,
		   statistic, df, p_value) %>% 
	gt() %>% 
	fmt_number(2:7) %>% 
	fmt_number(8, decimals = 3) %>% 
	cols_merge(starts_with("conf_"), pattern = "[{1}, {2}]") %>% 
	cols_label(
		term = md("**Predictor**"),
		estimate = md("**Estimate**"),
		std_error = md("**SE**"),
		conf_lower = md("**CI<sub>95%</sub>**"),
		statistic = md("***t***"),
		df = md("**df**"),
		p_value = md("***p***")
	) %>% 
	tab_style(
		style = list(
			cell_fill(color = "#F9E3D6")
		),
		locations = cells_body(
			columns = everything(),
			rows = p_value < 0.05
		)
	)
gtsave(data = main_effects, filename = "main_effects.png", path = here("Figures"))
main_effects
```

@@

augment(fit) %>% 
	mutate(.fitted_prob = logit_to_prob(.fitted)) %>% 
	ggplot() +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun.data = mean_se, geom = "ribbon", alpha = 0.5, colour = NA) +
	stat_summary(aes(x = ot1, y = .fitted_prob, colour = trial_type, fill = trial_type),
				 fun = mean, geom = "line", size = 1) +
	# stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	geom_text(data = sample_size,
			  aes(x = -0.3, y = 0.95, label = paste0("n = ", n)),
			  show.legend = FALSE,
			  colour = "black", fill = "black") +
	labs(x = "Time bin (100 ms)", y = "Prob. of target fixation",
		 colour = "Trial type", fill = "Trial type",
		 caption = "Marginal means of the multilevel model, plotted in separate panels for monolinguals and bilinguals, across age\ngroups. Sample sizes are indicated at the upper left corner in each panel. The first and last 300 ms in each trial\nwere trimmed before the analysis.") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) + 
	scale_x_continuous(breaks = unique(gaze$ot1), labels = unique(gaze$time_bin)) +
	theme_custom() +
	theme(
		legend.position = "top",
		axis.text = element_text(size = 7),
		plot.caption = element_text(size = 10, hjust = 0),
		plot.caption.position = "plot"
	) +
	ggsave(here("Figures", "emmeans.png"), height = 6)
```
